Computing with an Angry Poker Player

### 2014-09-25 draft0.tex
adding small insight to model of computation

@@

>>>>

The fact that we have a synchronizer means that the model of computation is equivalent to one where there is only one clock for all input bits.

@@

What does this mean? Well, in particular, it means that we cannot do much. In particular, we can't add, since $x + 1$ will act as the NOT operator on the lowest order bit. We can only compute boolean circuits in planar graphs.
